Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-18 paper/ijcai/paper.tex
abstract

\begin{abstract}
  Software debugging is important and challenging. This paper reports
  on a comprehensive study to reassess the impact of combining two
  very popular automated techniques for software fault
  localization--Dynamic Slicing and Spectrum-based Fault
  Localization. Our results show that \Fix{...}
\end{abstract}

@@

Software debugging is difficult. In particular, the task of locating the faulty
code (\ie{}, fault localization) is particularly challenging. For that reason,
countless automated techniques have been proposed in the past to reduce the cost
of fault localization~\cite{7390282}.

@@

\begin{figure}[h]
		\includegraphics[width=0.45\textwidth]{figures/performance.pdf}
		\caption{Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{}}
		\label{fig:diagnosis}
\end{figure}

\begin{table*}[h]
	\small
	\centering
	\begin{tabular}{@{}llll@{}}
\toprule
  & SFL                    & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 522.47     & 684.89   & 611.04   \\ \midrule
Median & 50.375      & 66.25               & 54.3                \\ \midrule
Variance & 1191.12      & 1361.83   & 1301.78    \\ \midrule
Shapiro-Wilk & \makecell{W = 0.48 \\ p-value = 1.10 x $10^{-26}$} & \makecell{W = 0.55 \\ p-value = 4.31 x $10^{-25}$} & \makecell{W = 0.52 \\ p-value = 6.23 x $10^{-26}$}  \\ \midrule
Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 28.97 \\ p-value = 5.13 x $10^{-7}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table*}

>>>>

\begin{abstract}
  Software debugging is difficult. One of its main challenges is the improvement of Spectrum-based Fault Localization (SBFL) scores accuracy. We suspect that several highly ranked statements - covered by failing executions - may be unrelated to the fault. This paper reports the results of a comprehensive study perfomed to reassess the impact of combining Dynamic Slicing with SBFL to improve Software Fault Localization, a technique we coin as Tandem-FL. We leverage the Mozzila's Lithium Slicer engine to minimize the top-5 and top-10 classes that comprise the highest scored faulty statements of the Defects4j failing tests. The SFL score is computed before and after applying DS to calculate the impact of Tandem-FL.
  Our results show that adding DS to SFL improves the diagnosis accuracy of SFL. 
\end{abstract}

@@

Software debugging is important and challenging. In particular, the task of locating the faulty
code (\ie{}, fault localization) is particularly challenging. For that reason,
countless automated techniques have been proposed in the past to reduce the cost
of fault localization~\cite{7390282}.

@@

\begin{figure}[h]
		\centering
		\includegraphics[width=0.42\textwidth]{figures/performance.pdf}
		\caption{Diagnosis Performance for using \combpar{5} and \combpar{10} instead of \sfl{}}
		\label{fig:diagnosis}
\end{figure}

\begin{table*}[h]
	\centering
	\begin{tabular}{@{}llll@{}}
\toprule
  & SFL                    & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 522.47     & 684.89   & 611.04   \\ \midrule
Median & 50.375      & 66.25               & 54.3                \\ \midrule
Variance & 1191.12      & 1361.83   & 1301.78    \\ \midrule
Shapiro-Wilk & \makecell{W = 0.48 \\ p-value = 1.10 x $10^{-26}$} & \makecell{W = 0.55 \\ p-value = 4.31 x $10^{-25}$} & \makecell{W = 0.52 \\ p-value = 6.23 x $10^{-26}$}  \\ \midrule
Friedman & \multicolumn{3}{c}{\makecell{$\chi^{2}$ = 28.97 \\ p-value = 5.13 x $10^{-7}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table*}
